### 2019-09-30 Sections/cryptowars.tex
restructure crypto assets
ZKP++
different blind and verification file
adding changes to QKD hacking

\if 2\pubmode
\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{QAB_long}
\captionspacefig \caption{Protocol for quantum anonymous broadcasting. (a) A central trusted server prepares GHZ states and distributes them amongst a group of users, one qubit per user. All users measure in the $\pm$-basis. (b) All users classically broadcast their measurement outcomes yielding shared random parity. During broadcast, the broadcaster lies about his measurement outcome to flip the joint parity if he wishes to transmit `1', or tells the truth to transmit `0'. The joint parity encodes the message of the anonymous user, which all listeners are able to recover. Importantly, only one user may broadcast at a time, otherwise the recovered message will be given by the XOR of all the simultaneously broadcast messages.} \label{fig:QAB}
\end{figure}
\else
\begin{figure*}[!htbp]
\includegraphics[clip=true, width=0.8\textwidth]{QAB}
\captionspacefig \caption{Protocol for quantum anonymous broadcasting. (a) A central trusted server prepares GHZ states and distributes them amongst a group of users, one qubit per user. All users measure in the $\pm$-basis. (b) All users classically broadcast their measurement outcomes yielding shared random parity. During broadcast, the broadcaster lies about his measurement outcome to flip the joint parity if he wishes to transmit `1', or tells the truth to transmit `0'. The joint parity encodes the message of the anonymous user, which all listeners are able to recover. Importantly, only one user may broadcast at a time, otherwise the recovered message will be given by the XOR of all the simultaneously broadcast messages.} \label{fig:QAB}
\end{figure*}
\fi

@@

\sectionby{Zixin Huang}

\dropcap{F}{or} a QKD system, information-theoretic security\index{Information-theoretic!Security} is achieved only when security against collective, coherent attacks is proven. We mustn't make assumptions about the limitations of our adversaries.

@@

\subsection{Trojan horse attacks}\index{Trojan horse attacks}

The family of Trojan horse attacks involves Eve probing the settings of Alice and Bob by sending light into their devices and collecting the reflected signal. The first of this kind of attack actually came for free for the eavesdropper \cite{bib:RevModPhys.81.1301}: it was discovered that some photon-counters emit light when a photon is detected \cite{bib:kurtsiefer2001breakdown}. If the emitted light carries correlated information about which detector was triggered, it must be prevented from leaking outside the secure space and becoming accessible to Eve.

@@

\subsection{Beamsplitter \& photon-number-splitting attacks}\index{Beamsplitter attacks}\index{Photon-number-splitting attacks}

If the state preparation consists of more than one photon, Eve can count the number of photons in each signal and act accordingly. Such attacks are called photon-number-splitting (PNS) attacks \cite{bib:PhysRevLett.68.3121}. The BS and PNS attacks were discovered as zero-error attacks against BB84 implemented with weak laser pulses. To counter the attack, the decoy-state\index{Decoy states} method \cite{bib:PhysRevLett.91.057901, bib:PhysRevLett.94.230504} was developed.

\subsection{Detector attacks}\index{Detector!Attacks}

@@

>>>>

\if 1\doublecol
\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{QAB_long}
\captionspacefig \caption{Protocol for quantum anonymous broadcasting. (a) A central trusted server prepares GHZ states and distributes them amongst a group of users, one qubit per user. All users measure in the $\pm$-basis. (b) All users classically broadcast their measurement outcomes yielding shared random parity. During broadcast, the broadcaster lies about his measurement outcome to flip the joint parity if he wishes to transmit `1', or tells the truth to transmit `0'. The joint parity encodes the message of the anonymous user, which all listeners are able to recover. Importantly, only one user may broadcast at a time, otherwise the recovered message will be given by the XOR of all the simultaneously broadcast messages.} \label{fig:QAB}
\end{figure}
\else
\begin{figure*}[!htbp]
\includegraphics[clip=true, width=0.8\textwidth]{QAB}
\captionspacefig \caption{Protocol for quantum anonymous broadcasting. (a) A central trusted server prepares GHZ states and distributes them amongst a group of users, one qubit per user. All users measure in the $\pm$-basis. (b) All users classically broadcast their measurement outcomes yielding shared random parity. During broadcast, the broadcaster lies about his measurement outcome to flip the joint parity if he wishes to transmit `1', or tells the truth to transmit `0'. The joint parity encodes the message of the anonymous user, which all listeners are able to recover. Importantly, only one user may broadcast at a time, otherwise the recovered message will be given by the XOR of all the simultaneously broadcast messages.} \label{fig:QAB}
\end{figure*}
\fi

@@

\sectionby{Zixin Huang}\index{Zixin Huang}

\dropcap{F}{or} a QKD system, information-theoretic security\index{Information-theoretic!Security} is achieved only when security against collective, coherent attacks is proven. We mustn't make assumptions about the limitations of our adversaries. For a more comprehensive review
on quantum cryptography, see Ref.~\cite{pirandola2019advances}.

@@

\subsection{Hacking discrete-variable protocols}

\subsubsection{Beamsplitter \& photon-number-splitting attacks}\index{Beamsplitter attacks}\index{Photon-number-splitting attacks}

The security proofs for many discrete variable protocols assumes that Alice's signals consist of single photons. However, true single-photon soures are not yet widely available, and QKD systems often make use of strongly-attenuated laser pulses, and there is some probability of the source emitting multiple photons. This fact can be exploited 
by Eve, who employs the photon number splitting (PNS) attack \cite{bib:PhysRevLett.68.3121}: Eve can perform a non-demolition measurement to determine the number of photons 
in the signal, she steals the excess photons and sends the rest to bob. She stores these in her quantum memory and wait until the classical communication between Alice and Bob, hence finding out Alice's preparation basis.

 % The BS and PNS attacks were discovered as zero-error attacks against BB84 implemented with weak laser pulses.

A method used to counter the PNS attack is the decoy-state\index{Decoy states} method \cite{bib:PhysRevLett.91.057901, bib:PhysRevLett.94.230504} . In the decoy-state protocol, Alice randomly replaces some of her signal states with multi-photon pulses from a decoy source. Eve cannot distinguish between decoy pulses from the encoding signals, and can only act identially on both. In the post-process stage, Alice public announces which states were the decoy pulses. The trusted parties can then characterise the action of the channel on the multiple-photon pulses and detect the presence of a PNS attack.

\subsubsection{Trojan horse and flash-back attacks}\index{Trojan horse attacks}

Another family of hacking that can be used against discrete-variable QKD is the Trojan horse attacks.
These attack involve Eve probing the settings of Alice and Bob by sending light into their devices and collecting the reflected signal. The first of this kind of attack actually came for free for the eavesdropper \cite{bib:RevModPhys.81.1301}: it was discovered that some photon-counters emit light when a photon is detected \cite{bib:kurtsiefer2001breakdown}. If the emitted light carries correlated information about which detector was triggered, it must be prevented from leaking outside the secure space and becoming accessible to Eve.

@@

\subsubsection{Detector attacks}\index{Detector!Attacks}

@@

\subsection{Attacks on continuous-variable protocols}

% Quantum Crypto-Assets

\input{Sections/quantum_crypto_assets}
